---
title: "Butterfly Package Tutorial"
author: "Kandace LeDuff"
date: "`r Sys.Date()`"
output: html_document
---

# An introduction to, Facilitating Butterfly Data, R package.

The following tutorial is based on the butterfly data set from R. This tutorial was created to show how we can condense the data from the butterlfly data set, using several functions. My r package is relatively simple, and its functions will allow us to calculate, vizualize and query/process data. 

### **Part 1: Installing and loading necessary packages**

The first step in this tutorial is to install and load any necessary packages into our r studio if we haven't already done so. The two packages we will need are *tidyverse* and *treedata.table*.

We can run the code as so for our tidyverse package:
```{r eval=FALSE, include=TRUE}
install.packages("tidyverse")
## And then load in our package:
library(tidyverse)
```

The code for our treedata.table can be run as:
```{r eval=FALSE, include=TRUE}
install.packages("treedata.table")
## Once again just to make sure everything is running smootlhy, we'll load in our package:
library(treedata.table)
```

If everything loaded correctly we'll move on to part 2.

### **Part 2: Reading in our data**

For this package, we will need to read in our butterfly data set. Most of us probably have it in our data folder already but if not we'll need to upload it there.

To do this we first will go to our original projects in our r studio. Under data we'll find the butterfly_data.csv set. After clicking on the white box to the left of the title we'll click the blue "more" cog and then click export. We'll then click download and save the file to our computer under butterfly_data.csv. Lastly we'll return to our initial project and click upload, which will place the data set in the folder we choose.

```{r}
## Our next step will be to make sure we run library tidyverse and then read in our data set. The code should be as follows:###
library(tidyverse)
 Butterfly_data <- read_csv("Butterfly_data.csv")
 view(Butterfly_data)
 
```

Now we will move on to our functions.

### **Part 3: Calculating mean function**

The first function we will use will allow us to calculate the mean of two temperatures. Because the Butterfly data set has a column for both Spring and Summer temperatures, I wanted to create a function that would help us find an average temperature between the two columns.

```{r}
calc_butterflytemp_mean <- function(sT, st) {
  temp_mean <- mean(sT * st/2) 
  return(temp_mean)
}

calc_butterflytemp_mean(6.85,15.35)
```

The function should've given us the value of *52.57375 * which is the mean of *6.85 * and *15.35*

# We can include text anywhere in the document, it must be commented because R will try to run it

![Caption](path/to/image)

It is possible to include [hyperlinks]()
